### 2021-03-28 final_report/include/CAMT.tex
fixed typos and other minor minor things

\subsection{The English corpus} \label{eng}
Even avoiding CP, the small size of these corpora, the limitations of the language models used for parsing and the issues encountered in the UD-to-GF conversion make both the lexica resulting from this process relatively small.
This, together with the issues GF parsing suffers from, discussed in Chapter \ref{ch2}, makes working on arbitrary sentences taken from documents similar to those the course plans corpora are composed of extremely hard. \smallskip

@@

Some errorsregarding the extracted concepts are also interesting to analyze.
In English-Swedish, while several compounds, such as $\langle$\textit{``computer science'', ``datavetenskap''}$\rangle$, are aligned correctly, there are cases in which a single-root noun is translated as a compound (e.g. $\langle$ \textit{``theory'', ``automatateori''} $\rangle$). This is not necessarily an actual alignment error, as it might rather be that the English version of the text was being less specific than its Swedish counterpart, thus producing an alignment that, during evaluation, would have been marked as ``correct but not reusable'' (\texttt{=}). \smallskip

>>>>

\subsection{The English corpus} \label{eng}
Even without CP, the small size of these corpora, the limitations of the language models used for parsing and the issues encountered in the UD-to-GF conversion make both of the lexica resulting from this process relatively small.
This, together with the issues GF parsing suffers from (as discussed in Chapter \ref{ch2}), makes working on arbitrary sentences extremely hard. Even only using sentences extracted from documents that are similar, both stylistically and in terms of content, to those the course plans corpora are composed of is not especially helpful. \smallskip

@@

Some errors regarding the extracted concepts are also interesting to analyze.
In English-Swedish, while several compounds, such as $\langle$\textit{``computer science'', ``datavetenskap''}$\rangle$, are aligned correctly, there are cases in which a single-root noun is translated as a compound (e.g. $\langle$ \textit{``theory'', ``automatateori''} $\rangle$). This is not necessarily an actual alignment error, as it might well be the case that the English version of the text was being less specific than its Swedish counterpart, thus producing an alignment that, during evaluation, would have been marked as ``correct but not reusable'' (\texttt{=}). \smallskip

### 2021-03-28 final_report/include/CE.tex
fixed typos and other minor minor things

Obviously, the ``full-sentence'' tree pair is itself an alignment, even though a trivial one, as it represents a sentence-level correspondence in a case where, due to the approach being syntactic comparison, the inputs are assumed to be sentences that correspond to each other\footnote{Contrary to what it may seem, however, sentence-level alignment is in general not at a trivial task, as it is often the case, especially in certain language pairs, that one \textit{orthographic} sentence, i.e. a sentence defined based on the presence of a full stop, maps to more than one orthographic sentences in the translated text, or vice versa.}.

@@

\subparagraph*{Conflational divergence} \label{confl}
Conflational divergences involve the translation of two or more words in the source language using a single word that combines their meanings in the target language. A straightforward example is that of compounds, for instance
\begin{example} 
 ``Filippo is interested in \underline{game development}'' VS ``Filippo är intresserad av \underline{spelutveckling}''
\end{example}
but there are also other cases, like
\begin{example} 
 ``I'll come and \underline{say hello} to Bruno and Andrea'' VS ``Verrò a \underline{salutare} Bruno e Andrea''
\end{example} 
where the single word ``\textit{salutare}'' is not a compound but expresses the same meaning as ``\textit{say}'' and ``\textit{hi}'' together. \smallskip
Divergences like the one described in the latter example are usually captured by Criterion \ref{udmatch}, while compounds often need to be taken care of explicitly. For reasons that will become clear later, these cases are discussed in Section \ref{heads}.

>>>>

Obviously, the ``full-sentence'' tree pair is itself an alignment, even though a trivial one, as it represents a sentence-level correspondence in a case where, due to the approach being syntactic comparison, the inputs are assumed to be sentences that correspond to each other\footnote{Contrary to what it may seem, however, sentence-level alignment is in general not na trivial task, as it is often the case, especially in certain language pairs, that one \textit{orthographic} sentence, i.e. a sentence defined based on the presence of a full stop, maps to more than one orthographic sentences in the translated text, or vice versa.}.

@@

\subparagraph*{Conflational divergence} \label{confl}
Conflational divergences involve the translation of two or more words in the source language using a single word that combines their meanings in the target language. A straightforward example is that of compounds, for instance
\begin{example} 
 ``Filippo is interested in \underline{game development}'' VS ``Filippo är intresserad av \underline{spelutveckling}''
\end{example}
but there are also other cases, like
\begin{example} 
 ``I'll come and \underline{say hi} to Bruno and Andrea'' VS ``Verrò a \underline{salutare} Bruno e Andrea''
\end{example} 
where the single word ``\textit{salutare}'' is not a compound but expresses the same meaning as ``\textit{say}'' and ``\textit{hi}'' together. \smallskip
Divergences like the one described in the latter example are usually captured by Criterion \ref{udmatch}, while compounds often need to be taken care of explicitly. For reasons that will become clear later, these cases are discussed in Section \ref{heads}.

### 2021-03-28 final_report/include/Conclusions.tex
fixed typos and other minor minor things

\subsection*{Further integration with statistical alignment techniques} 
With regards to the CA component itself, it is important to remember that both the quantity and the quality of the alignments are a direct consequence of those of the dependency trees they are obtained from. 
Apart from working on dependency parsers directly, a possibility is to experiment more with hybrid alignment approaches, integrating the results prodiced by statistical tools (which only depend on the quantity and quality of raw data rather than also on that of their analyses) with those of our rule-based system. 
A basic way to do that has already been implemented, but has not been made use of in the final MT experiments due to the small size of the corpora involved.

>>>>

\subsection*{Further integration with statistical alignment techniques} 
With regards to the CA component itself, it is important to remember that both the quantity and the quality of the alignments are a direct consequence of those of the dependency trees they are obtained from. 
Apart from working on dependency parsers directly, a possibility is to experiment more with hybrid alignment approaches, integrating the results produced by statistical tools (which only depend on the quantity and quality of raw data rather than also on that of their analyses) with those of our rule-based system. 
A basic way to do that has already been implemented, but has not been made use of in the final MT experiments due to the small size of the corpora involved.

### 2021-03-28 final_report/include/TT.tex
fixed typos and other minor minor things

As mentioned in the introduction, the task of aligning concepts comes in two variants:
\begin{enumerate}
    \item \textbf{\textit{Concept Extraction}} (CE), which consists in identifying new concepts via linguistic comparison and whose output is a set of bilingual alignments
    \item \textbf{\textit{Concept Propagation}} (CP), i.e. the task of finding the concrete expressions corresponding to a set of known concepts in a particular language. Here, by concepts we do not mean necessarily ASTs, as a suitable approach is to propagate UD tree alignments before obtaining the corresponding abstract representation.
\end{enumerate} \smallskip

@@

As mentioned in the introduction, however, alignment can be performed at different levels of abstraction: to bring this to the extreme, there are contexts in which we might want to align full sentences, or even whole documents. While the latter two levels of abstraction are not necessarily relevant to MT, only aligning individual words is also, as discussed in the Introduction, not always the best option. For this reason, word alignment is often generalized to \textit{phrase alignment}. In systems like GIZA++, whose output is a list of pairs of word positions indicating which words in the SL string are to be aligned with which words in the TL string (commonly referred to as the \textit{pharaoh format}), extracting phrase alignments by combining the indices is realtively straightforward. \smallskip

>>>>

As mentioned in the Introduction, the task of aligning concepts comes in two variants:
\begin{enumerate}
    \item \textbf{\textit{Concept Extraction}} (CE), which consists in identifying new concepts via linguistic comparison and whose output is a set of bilingual alignments
    \item \textbf{\textit{Concept Propagation}} (CP), i.e. the task of finding the concrete expressions corresponding to a set of known concepts in a particular language. Here, by concepts we do not mean necessarily ASTs, as a suitable approach is to propagate UD tree alignments before obtaining the corresponding abstract representation.
\end{enumerate} \smallskip

@@

As mentioned in the Introduction, however, alignment can be performed at different levels of abstraction: to bring this to the extreme, there are contexts in which we might want to align full sentences, or even whole documents. While the latter two levels of abstraction are not necessarily relevant to MT, only aligning individual words is also, as discussed in the Introduction, not always the best option. For this reason, word alignment is often generalized to \textit{phrase alignment}. In systems like GIZA++, whose output is a list of pairs of word positions indicating which words in the SL string are to be aligned with which words in the TL string (commonly referred to as the \textit{pharaoh format}), extracting phrase alignments by combining the indices is realtively straightforward. \smallskip
